---
title: "Driving Hazards"
output:
  html_document:
    df_print: paged
---
[Code repository](https://github.com/introdsci/DrivingHazards) and [Published copy](https://introdsci.github.io/DrivingHazards/)

Let's look into the `Seatbelts` built-in data set to explore information about driving hazards. First, I am loading the data set into a table and converting the `law` variable into a logical type (`TRUE` or `FALSE`) instead of a numeric (`0` or `1`) value.

```{r echo=TRUE, message=FALSE, error=FALSE, warning=FALSE}
library("dplyr")
library("tidyr")
library("caret")

driving <- as_tibble(Seatbelts)
driving$law <- as.logical(driving$law)
```

But let's also look at the total number of people killed (not separated by seat).

```{r}
driving$totalKilled <- driving$DriversKilled+driving$front+driving$rear
```

Finally, let's explore what variables help us predict the number of deaths due to car accidents.

```{r}
driving_model <- lm(data=driving, formula=totalKilled~drivers+kms+PetrolPrice+law)
summary(driving_model)
```

Note that the (logical) `law` variable has automatically been created as a *dummy variable* and incorporated in the regression equation as `**lawTRUE**. In other words, whether or not there is a law on seatbelts in place contributes to the prediction (*p<.01*) of how many auto fatalities there are (*reducing* the predicted deaths by about **128.5**).
